ManuscriptFigures

### 2024-02-26 Code/ManuscriptFigures.Rmd
Changed 4hr photoperiod shape to solid square

MyPhotoperiods = as.factor(c(4, 8, 12, 16))
PhotoperiodShapes = c(6, 18, 16, 17)

@@

MED4PAR <- PURPARFits %>%
   filter(Strain == "MED4",
           Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")
MED4PAR

SS120PAR <- PURPARFits %>%
   filter(Strain == "SS120",
          Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")

@@

MIT9313PAR <- PURPARFits %>%
   filter(Strain == "MIT9313",
            Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
   mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")

@@

          Strain == "MED4" &  Par_ue == 30 & WL == "660"& Run == 109 ~ 1,

>>>>

MyPhotoperiods = as.factor(c(4, 8, 12, 16))
PhotoperiodShapes = c(15, 18, 16, 17)

@@

MED4PAR <- PURPARFits %>%
   filter(Strain == "MED4",
           Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 28, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 28, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")
MED4PAR

SS120PAR <- PURPARFits %>%
   filter(Strain == "SS120",
          Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 28, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 28, color = "black", vjust = 1.0),
       # axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")

@@

MIT9313PAR <- PURPARFits %>%
   filter(Strain == "MIT9313",
            Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
   mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 28, color = "black", vjust = 1.0),
       axis.title.y = element_text(size = 28, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")

@@

          Strain == "MED4" &  Par_ue == 30 & WL == "660"& Run == 99 ~ 1,
